---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Access to clean fuels for cooking vs GDP per capit


## Yuwei Jiang + 32307322

This is a template that contains materials to create a shiny gadget application
for assessment 2. You will need the following packages installed to 
generate the gadget from this template:

```{r, eval = FALSE}
install.packages(c("shiny", "crosstalk", "plotly", "DT", "tidyverse", "here", "ggplot2"))
```

## How to run the app
   
In this shiny app, you can explore the relationships between the wealth of a country and the 
proportion of the population that have access to clean cooking fuels.   
On the chart page, you can select one or more countries and move the year slider to explore the data. And you have the choice to hide data points on countries where there are less than 1 million in the upper right. The app also allow you to toggle between a linear axis and a log axis on the chart. On the table page, it shows all the years for each country ordered by from most recent year. And the table could update according to a change from the selection input provided by this shiny app. 


## Session Info

 setting  value                         
 version  R version 4.0.5 (2021-03-31)  
 os       Windows 10 x64                
 system   x86_64, mingw32               
 ui       RStudio                       
 language (EN)                          
 collate  Chinese (Simplified)_China.936
 ctype    Chinese (Simplified)_China.936
 tz       Australia/Sydney              
 date     2021-09-24                    



